\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-09 doc/sw-system.tex
fixes and close #113.
Added full description of HumVI settings top section 3.2, closes #117

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band images
were also available for perusal in Talk). We made colour composite PNG format
images\footnote{The open source colour image composition code used in this work
is available from \texttt{http://github.com/drphilmarshall/HumVI}} following the
prescription of \citet{LuptonEtal2004} \citep[with extensions
by]{WherryEtal2004}. Specifically, we first rescaled the pixel values of each
channel image into flux units, and then applied an arcsinh stretch. The stretch
parameters were optimized by visually inspecting a small randomly-selected
sample of images, to ensure that the background noise was just visible,  and
that the centres of bright, intermediate redshift galaxies were not saturated.
The color scales were chosen to maximize the contrast between faint extended
objects. These parameters were then fixed during the production of all the
tiles, in order to allow straightforward comparison between one image and
another, and for intuition to be built up about the appearance of stars and
galaxies across the survey. Alternative algorithms, such as adjusting the
stretch and scale dynamically according to, for example, the root-mean-square
pixel value in each image, can lead to better presentation of bright objects,
but in doing so they tend to hide the faint features in those images: we needed
to optimize the detectability of these faint features.   Examples of CFHTLS
training set images prepared in this way can be seen in the galleries of the
previous section (Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of visualization parameters, to display a ``bluer'' image and a ``brighter'' image in the classification interface Quick Dashboard (\Sref{sec:design:interface}). The QD code performs the same image composition as just described, but dynamically on FITS images in the browser. These FITS images are also available for viewing in Talk, via the main Zooniverse Dashboard image display tool, which again offers the same stretch settings, as a starting point for image exploration.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band
images were also available for perusal in Talk). \new{We made colour composite PNG
format images
following the prescription of \citet{LuptonEtal2004} \citep[with extensions
by][and some particular choices of our own]{WherryEtal2004}, using the \humvi
software.\footnote{The \humvi colour image composition code used in
this work is open source and available from \texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we
first rescaled the pixel values of each image, in the notation of
\citeauthor{LuptonEtal2004}) into flux units (``picomaggies,''), via the image
AB zeropoint $m_0$ and the pixel value calibration factor $f$  given by
$\log_{10}{f} = 0.4(30.0 - m_0)$. We then applied further aesthetic
``scales'' $s_{i,r,g}$ before computing the intensity image $I$ and applying
an arcsinh stretch. (The scales are re-normalized to sum to one.) Thus, the red
($R$), green ($G$) and blue ($B$) channel images correspond to the CFHTLS $i$,
$r$ and $g$-band images in the following way:
\bea
I & = & (i \cdot s_i + r \cdot s_r + g \cdot s_g), \notag \\
R & = & i \cdot s_i \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
G & = & r \cdot s_r \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
B & = & g \cdot s_g \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}. \notag \\
\eea
We chose to allow the composite image formed from these channel images to
saturate to white: any pixels in any of the channel images lying outside the
range 0 to 1 was assigned the value 0 or 1 appropriately. This was not the
recommendation of \citet{LuptonEtal2004}, but we found it to give very
informative but also familiar-looking astronomical images.}

\new{The non-linearity parameters $Q$ and $\alpha$ control the brightness and
contrast of the images. We first tuned $\alpha$ (which acts as an additional
scale factor) until the background noise was just visible. Then we tuned the
colour scales $s$ to find a balance between exposing the low surface
brightness blue features (important for lens spotting!), and having the noise
appear to have equal red, green and blue components. Non-linearity sets in at
about $1/(Q \alpha)$ in the  scaled intensity image: finally, tuning $Q$ at
fixed $\alpha$ determines the appearance of bright galaxies, which we need to
be suppressed enough to allow the low surface brightness features to show
through, but not so much that they no longer looked like massive galaxies.}

These parameters were then fixed during the production of all the tiles, in
order to allow straightforward comparison between one image and another, and
for intuition to be built up about the appearance of stars and galaxies across
the survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of CFHTLS training set
images prepared in this way can be seen in the galleries of the previous
section (Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of
visualization parameters, to display a ``bluer'' image and a ``brighter''
image in the classification interface Quick Dashboard
(\Sref{sec:design:interface}). The QD code performs the same image composition
as just described, but dynamically on FITS images in the browser. These FITS
images are also available for viewing in Talk, via the main Zooniverse
Dashboard image display tool, which again offers the same stretch settings, as
a starting point for image exploration. Our parameter choices are given in
\Tref{tab:data:humvi}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\begin{center}
\caption{Example \humvi image display parameters, for the CFHTLS images.}
\label{tab:data:humvi}
\begin{tabular}{cccc}
  \hline
  \hline {Image} & Scales ${s_i,s_r,s_g}$ & $\alpha$ & $Q$ \\                         
  \hline
    ``Standard'' &    ${0.4,0.6,1.7}$     &   0.09   & 1.0 \\
    ``Brighter'' &    ${0.4,0.6,1.7}$     &   0.17   & 1.0 \\
       ``Bluer'' &    ${0.4,0.6,2.5}$     &   0.11   & 2.0 \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table}
% Quck Dashboard code: https://github.com/zooniverse/Lens-Zoo/blob/vics82/app/controllers/quick_dashboard.coffee
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
